---
title: "Model Card: Sydney Beach Water Temperature GAM"
date: '`r Sys.Date()`'
output: 
  html_document
params:
    name: "sydney-beach-gam"
    board: !r pins::board_folder(path = here::here("inst/deploy"))
---

```{r setup, include=FALSE}
library(vetiver)
library(pins)
library(here)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)

deploy_board <- pins::board_folder(path = here("inst/deploy"))

v <- vetiver_pin_read(params$board, params$name)
v_meta <- pin_meta(params$board, params$name)
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

- Developed by PERSON AND/OR TEAM
- `r cli::pluralize("{v$description} using {ncol(v$prototype)} feature{?s}")`
- More details about how model was developed and what it is predicting
- More details on feature engineering and/or data preprocessing for model
- Version `r v$metadata$version` of this model was published at `r v_meta$created`
- Citation and/or license details for the model
- If you have questions about this model, please contact PERSON@ORG.ORG

## Intended use

- The primary intended uses of this model are ...
- The primary intended users of this model are ...
- Some use cases are out of scope for this model, such as ...

## Important aspects/factors

- Aspects or factors (demographic, environmental, technical) that are relevant to the context of this model are ...
- In evaluating this model, we examined aspects such as ...

## Metrics

- The metrics used to evaluate this model are ...
- These metrics are computed via ...
- We chose these metrics because ...

## Training data & evaluation data

- The training dataset for this model was ...
- The training dataset for this model has the "prototype" or signature:

    ```{r}
    glimpse(v$prototype)
    ```


## Ethical considerations

- We considered ...

## Caveats & recommendations

- This model does ...
- This model does not ...
- We recommend ...



